Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-06 submission.tex
changes to paragraph on pronouns in tag set experiments

\paragraph{Pronouns}
Pronouns in Norwegian are personal, reciprocal, reflexive and interrogative.
They can furthermore exhibit gender, number and person, while personal pronouns
can be distinguished case (accusative or nominative).

The results in Table \ref{pronresults} show that number, person and type are
the most informative features for parsing, with LAS of 87.21\%, 87.22\% and
87.19\%, respectively. However, when combining number and person, we observe a
drop by more than 0.2 percentage points, indicating that these features do not
interact in any syntactically distinctive way. The most interesting observation
is that all experiments exceed the tagging accuracy of the original tag set,
the most improved being the most fine-grained distinction, namely type, case
and number combined, obtaining a tagger accuracy of 97.52\%. This shows that
the introduction of more fine-grained distinctions for pronouns is beneficial
and aids the PoS tagger in disambiguating ambiguous words. While case alone
yields an LAS of 87.08\%, we found that the combination of type and case, which
is the most successful experiment in terms of parser performance, yields the
second highest tagging accuracy of 97.51\%. The reason for this is that
pronouns of different type and personal pronouns of different case exhibit
quite different properties and appear in different constructions. Pronouns in
nominative case (i.e., subjects) primarily occur before the main verb, while
pronouns in accusative case (i.e., objects) occur after the main verb, as
Norwegian exhibits so-called V2 word order, requiring that the finite verb of a
declarative clause appears in the second position, hence its name. The
combination of type and number comes in close to the performance of type and
case, with LAS of 87.27\% and UAS identical to that of type and case.

>>>>

\paragraph{Pronouns}
Pronouns in Norwegian are personal, reciprocal, reflexive and interrogative.
They can furthermore exhibit gender, number and person, while personal pronouns
can be distinguished on case (either accusative or nominative).

The results in Table \ref{pronresults} show that number, person and type are
the most informative features for parsing, with LAS of 87.21\%, 87.22\% and
87.19\%, respectively. However, when combining number and person, we observe a
drop by more than 0.2 percentage points, indicating that these features do not
interact in any syntactically distinctive way. The most interesting observation
is that all experiments exceed the tagging accuracy of the original tag set,
the most improved being the most fine-grained distinction, namely type, case
and number combined, obtaining a tagger accuracy of 97.52\%. This shows that
the introduction of more fine-grained distinctions for pronouns aids the PoS
tagger in disambiguating ambiguous words. While case alone yields an LAS of
87.08\%, we found that the combination of type and case, which is the most
successful experiment in terms of parser performance, yields the second highest
tagging accuracy of 97.51\%. Pronouns of different type and personal pronouns
of different case exhibit quite different properties and appear in different
constructions. Pronouns in nominative case (i.e., subjects) primarily occur
before the main verb, while pronouns in accusative case (i.e., objects) occur
after the main verb, as Norwegian exhibits so-called V2 word order, requiring
that the finite verb of a declarative clause appears in the second position,
hence its name. The combination of type and number comes in close to the
performance of type and case, with LAS of 87.27\% and UAS identical to that of
type and case.
